State-Space Model to Estimate Salmon Escapement Using Multiple Data Sources

### 2020-09-12 analysis/paper/paper.Rmd
re-knit all 3 versions

```{r lgr-sim-tab}
crossing(`Trap rate` = c('0.15', 
                         "0.15 and 0.00 3 weeks"),
         `Fallback & Re-ascension rate` = c(0.06,
                             0.10),
         # `Re-ascension rate` = 1,
         `Window count error` = factor(c("No Error",
                                         "5% Error",
                                         "10% Error"),
                                       levels = c("No Error",
                                                  "5% Error",
                                                  "10% Error"))) %>%
  mutate(`Nighttime passage rate` = if_else(`Fallback & Re-ascension rate` == 0.06,
                                            0.06,
                                            0.05)) %>%
  mutate(Scenario = paste(rep(c('Baseline',
                                "N-R",
                                "N-R trap down",
                                "Trap down"),
                              each = 3)),
         Scenario = if_else(`Window count error` == "5% Error",
                            paste(Scenario, "Err L"),
                            if_else(`Window count error` == "10% Error",
                                    paste(Scenario, "Err H"),
                                    Scenario))) %>%
  select(Scenario, 
         `Trap rate`:`Fallback & Re-ascension rate`,
         `Nighttime passage rate`,
         `Window count error`) %>%
  kable(digits = 2,
        booktabs = T,
        caption = "Summary of simulation scenarios including varying adult trapping, fallback and re-ascension rates, nighttime passage, and window count error rates use to evaluate the performance of STADEM.") %>%
  kable_styling()

@@

```{r summ-tab}
sum_tab <- res_long_df %>%
  filter(Variable == 'Unique.Wild.Fish',
         Model == 'STADEM') %>%
  group_by(Scenario) %>%
  summarise(inCI = sum(inCI),
            nsims = n(),
            Sample_Mean = mean(est),
            `Relative bias` = mean(rel_bias),
            SE = sqrt(var(est)),
            `Mean CV` = mean(cv),
            # RMSD = sqrt(var(est) + mean(bias)^2),
            RMSE = sqrt(mean(bias^2)),
            MAE = mean(abs(bias)),
            Coverage = inCI/nsims) %>%
  mutate(Scenario = str_replace_all(Scenario,
                                    "_", " "),
         Scenario = str_replace(Scenario,
                                "TrapDown",
                                "Trap Down")) %>%
  select(Scenario,
         `Relative bias`,
         `Mean CV`,
         # RMSD,
         RMSE,
         # MAE,
         Coverage)

# mu_rmse <- sum_tab %>%
#   group_by(Model) %>%
#   summarise(mu = mean(RMSE))

sum_tab %>%
  kable(digits = 3,
        booktabs = T,
        caption = "Summary statistics, including relative bias, mean coefficient of variation (CV), root mean squared error (RMSE) and 95% credible interval coverage for results from each of the twelve simulation scenarios.") %>%
  kable_styling()
```

```{r lgr-tab}
lgr_est %>%
  mutate(prnt_val = if_else(is.na(cv),
                            as.character(prettyNum(round(mean), big.mark = ',')),
                            paste0(prettyNum(round(mean), big.mark = ","), " (", round(cv, 3), ")"))) %>%
  pivot_wider(id_cols = c("Species",
                          "Year"),
              names_from = "variable",
              values_from = "prnt_val") %>%
  select(Species, 
         Year,
         `Window counts` = win_cnt,
         Total = X.tot.new.all,
         Wild = X.tot.new.wild,
         Hatchery = X.tot.new.hatch,
         `Hatchery no-clip` = X.tot.new.hnc) %>%
  kable(booktabs = T,
        caption = "Window counts, and estimates of total, wild, hatchery and hatchery no-clip escapement, with coefficients of variation in parenthesis, for Chinook Salmon and steelhead from spawn years 2010 to 2019.") %>%
  kable_styling()
```

>>>>

```{r lgr-sim-tab}
crossing(`Trap rate` = c('0.15', 
                         "0.15 and 0.00 3 weeks"),
         `Fallback & Re-ascension rate` = c(0.06,
                             0.10),
         # `Re-ascension rate` = 1,
         `Window count error` = factor(c("No Error",
                                         "5% Error",
                                         "10% Error"),
                                       levels = c("No Error",
                                                  "5% Error",
                                                  "10% Error"))) %>%
  mutate(`Nighttime passage rate` = if_else(`Fallback & Re-ascension rate` == 0.06,
                                            0.06,
                                            0.05)) %>%
  mutate(Scenario = paste(rep(c('Baseline',
                                "N-R",
                                "N-R trap down",
                                "Trap down"),
                              each = 3)),
         Scenario = if_else(`Window count error` == "5% Error",
                            paste(Scenario, "Err L"),
                            if_else(`Window count error` == "10% Error",
                                    paste(Scenario, "Err H"),
                                    Scenario))) %>%
  select(Scenario, 
         `Trap rate`:`Fallback & Re-ascension rate`,
         `Nighttime passage rate`,
         `Window count error`) %>%
  kable(digits = 2,
        booktabs = T,
        linesep = "",
        caption = "Summary of simulation scenarios including varying adult trapping, fallback and re-ascension rates, nighttime passage, and window count error rates use to evaluate the performance of STADEM.") %>%
  kable_styling(latex_options = c('scale_down',
                                  "hold_position"))

@@

```{r summ-tab}

sum_tab <- res_long_df %>%
  filter(Variable == 'Unique.Wild.Fish',
         Model == 'STADEM') %>%
  group_by(Scenario) %>%
  summarise(inCI = sum(inCI),
            nsims = n(),
            Sample_Mean = mean(est),
            `Relative bias` = mean(rel_bias),
            SE = sqrt(var(est)),
            `Mean CV` = mean(cv),
            RMSE = sqrt(mean(bias^2)),
            Coverage = inCI/nsims) %>%
  mutate(Scenario = str_replace_all(Scenario,
                                    "_", " "),
         Scenario = str_replace(Scenario,
                                "TrapDown",
                                "Trap Down")) %>%
  select(Scenario,
         `Relative bias`,
         `Mean CV`,
         RMSE,
         Coverage)

sum_tab %>%
  kable(digits = c(0, 3, 3, 0, 3),
        booktabs = T,
        linesep = "",
        caption = "Summary statistics, including relative bias, mean coefficient of variation (CV), root mean squared error (RMSE) and 95 credible interval coverage for results from each of the twelve simulation scenarios.") %>%
  kable_styling(latex_options = c('scale_down',
                                  "hold_position"))

```{r lgr-tab}
lgr_est %>%
  mutate(prnt_val = if_else(is.na(cv),
                            as.character(prettyNum(round(mean), big.mark = ',')),
                            paste0(prettyNum(round(mean), big.mark = ","), " (", round(cv, 3), ")"))) %>%
  pivot_wider(id_cols = c("Species",
                          "Year"),
              names_from = "variable",
              values_from = "prnt_val") %>%
  select(Species, 
         Year,
         `Window counts` = win_cnt,
         Total = X.tot.new.all,
         Wild = X.tot.new.wild,
         Hatchery = X.tot.new.hatch,
         `Hatchery no-clip` = X.tot.new.hnc) %>%
  kable(booktabs = T,
        linesep = "",
        caption = "Window counts, and estimates of total, wild, hatchery and hatchery no-clip escapement, with coefficients of variation in parenthesis, for Chinook Salmon and steelhead from spawn years 2010 to 2019.") %>%
  kable_styling(latex_options = c('scale_down',
                                  "hold_position"))
